### 2005-11-21 doc/EFA/efa.tex
*** empty log message ***

Formally we define the synchronous product $A||B$ of two EFA's
\begin{eqnarray}
A=\langle Q^A, \Sigma^A, \delta^A, q^A_i, Q^A_m, X^{A},
G^A,x^A_0,X^A_m \rangle
\end{eqnarray} and \begin{eqnarray} B=\langle Q^B, \Sigma^B, \delta^B, q^B_i,
Q^B_m, X^{B}, G^B,x^B_0,X^B_m \rangle
\end{eqnarray} as
\begin{eqnarray}
A||B&=&\langle Q^A\times Q^B, \Sigma^A \cup \Sigma^B ,
\delta^{A||B}, (q^A_i,q^B_i) ,\nonumber\\
&& Q^A_m\times Q^B_m, X^A \times X^B, G^{A||B},(x^A_0,x^B_0),
X^A_m \times X^B_m \rangle.
\end{eqnarray}
To define the guard functions, the action functions and the
transition function of the product we make use of the
corresponding functions in $A$ and $B$. To denote the elements of
$A||B$ we remove unnecessary  superscripts and write $A||B=\langle
Q, \Sigma, \delta, q_i, Q_m, X, G ,x_0, X_m \rangle$. The guard
functions $g_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{guard_sync_1}
g_{q \sigma}(x)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}) \quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(x^{A})\quad\quad\quad\quad\quad\quad\quad\sigma\in \Sigma^A\setminus\Sigma^B\\
g_{q^B\sigma}(x^{B})\quad\quad\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
If any one of the guards functions in the above definition are
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation further, we use "dummy"
guard functions in the following way. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional guards functions
$g_{q^B\sigma}(.)=1$ for $B$ and if $\sigma\in\Sigma^B\setminus
\Sigma^A$ we set $g_{q^A\sigma}(.)=1$. Doing this, we can write
equation (\ref{guard_sync_1}) as
\begin{eqnarray}
g_{q \sigma}(x)= g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}).
\end{eqnarray}
The updating functions $a_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{action_sync_1}
a_{q \sigma}(x)=\left\{
\begin{array}{ll}
 \big(a^A_{q^A \sigma}(x^{A}), a^B_{q^B \sigma}(x^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a^A_{q^A\sigma}(x^{A}),x^{B}\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^A\setminus\Sigma^B\\
\big(x^{A},a^B_{q^B\sigma}(x^{B})\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions (\ref{guard_sync_1}),
the notion of being undefined is inherited from the action
functions of $A$ and $B$. Similar to the "dummy" guard functions
we introduce fictional action functions. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional action functions
$a_{q^B\sigma}(x^B)=x^B$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(x^A)=x^A$. With this convention equation
(\ref{action_sync_1}) simplifies to
\begin{eqnarray}
a_{q \sigma}(x)=
 \big(a^A_{q^A \sigma}(x^{A}), a^B_{q^B \sigma}(x^{B})\big).
\end{eqnarray}

 The transition function
$\delta(q,\sigma,x)$ is defined from $\delta^A$ and $\delta^B$ as
\begin{eqnarray}
\delta(q,\sigma,x)=\left\{
\begin{array}{ll}
\big(\delta^A(q^A,\sigma),\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad \sigma\in \Sigma^A \cap \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(\delta^A(q^A,\sigma),q^B,a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^A \setminus \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(q^A,\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^B \setminus \Sigma^A \quad g_{q \sigma}(x)=1\\
\textrm{
undefined}\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
g_{q\sigma}(x)=0
\end{array}\right.
\end{eqnarray}

>>>>

Formally we define the synchronous product $A||B$ of two EFA's
\begin{eqnarray}
A=\langle Q^A, \Sigma^A, \delta^A, q^A_i, Q^A_m, X^{A},
G^A,x^A_0,X^A_m \rangle
\end{eqnarray} and \begin{eqnarray} B=\langle Q^B, \Sigma^B, \delta^B, q^B_i,
Q^B_m, X^{B}, G^B,x^B_0,X^B_m \rangle
\end{eqnarray} as
\begin{eqnarray}
A||B&=&\langle Q^A\times Q^B, \Sigma^A \cup \Sigma^B ,
\delta^{A||B}, (q^A_i,q^B_i) ,\nonumber\\
&& Q^A_m\times Q^B_m, X^A \times X^B, G^{A||B},(x^A_0,x^B_0),
X^A_m \times X^B_m \rangle.
\end{eqnarray}
To define the guard functions, the action functions and the
transition function of the product we make use of the
corresponding functions in $A$ and $B$. To denote the elements of
$A||B$ we remove unnecessary  superscripts and write $A||B=\langle
Q, \Sigma, \delta, q_i, Q_m, X, G ,x_0, X_m \rangle$. The guard
functions $g_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{guard_sync_1}
g_{q \sigma}(x)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}) \quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(x^{A})\quad\quad\quad\quad\quad\quad\quad\sigma\in \Sigma^A\setminus\Sigma^B\\
g_{q^B\sigma}(x^{B})\quad\quad\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
If in any of the three cases, the corresponding guard function is
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation and increase readability,
we use "dummy" guard functions in the following way. If $\sigma\in
\Sigma^A \setminus \Sigma^B$ we introduce fictional guards
functions $g_{q^B\sigma}(.)=1$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set $g_{q^A\sigma}(.)=1$.
Doing this, we can write equation (\ref{guard_sync_1}) as
\begin{eqnarray}
g_{q \sigma}(x)= g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B}).
\end{eqnarray}
The updating functions $a_{q \sigma}(x)$ are defined as
\begin{eqnarray}\label{action_sync_1}
a_{q \sigma}(x)=\left\{
\begin{array}{ll}
 \big(a_{q^A \sigma}(x^{A}), a_{q^B \sigma}(x^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a_{q^A\sigma}(x^{A}),x^{B}\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^A\setminus\Sigma^B\\
\big(x^{A},a_{q^B\sigma}(x^{B})\big)\quad\quad\quad\quad\quad\sigma\in\Sigma^B\setminus\Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions (\ref{guard_sync_1}),
the notion of being undefined is inherited from the action
functions of $A$ and $B$. Similar to the "dummy" guard functions
we introduce fictional action functions. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional action functions
$a_{q^B\sigma}(x^B)=x^B$ for $B$ and if
$\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(x^A)=x^A$. With this convention equation
(\ref{action_sync_1}) simplifies to
\begin{eqnarray}
a_{q \sigma}(x)=
 \big(a_{q^A \sigma}(x^{A}), a_{q^B \sigma}(x^{B})\big).
\end{eqnarray}

 The transition function $\delta^{A||B}$ is defined from $\delta^A$ and $\delta^B$ as
\begin{eqnarray}
\delta^{A||B}(q,\sigma,x)=\left\{
\begin{array}{ll}
\big(\delta^A(q^A,\sigma),\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad \sigma\in \Sigma^A \cap \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(\delta^A(q^A,\sigma),q^B,a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^A \setminus \Sigma^B \quad g_{q \sigma}(x)=1\\
\big(q^A,\delta^B(q^B,\sigma),a_{q \sigma}(x)\big) \quad\quad\quad\quad\quad \sigma\in \Sigma^B \setminus \Sigma^A \quad g_{q \sigma}(x)=1\\
\textrm{
undefined}\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
g_{q\sigma}(x)=0
\end{array}\right.
\end{eqnarray}

\subsubsection{Properties of the product}
$(A||B)||C$:

\begin{eqnarray}
g^{(A||B)||C}_{q \sigma}(x)&=& g_{q^{AB}\sigma}(x^{AB})\wedge
g_{q^C\sigma}(x^{C})\nonumber\\
&=&g_{q^A\sigma}(x^{A})\wedge g_{q^B\sigma}(x^{B})\wedge
g_{q^C\sigma}(x^{C})\nonumber\\
&=& g_{q^{A}\sigma}(x^{A})\wedge g_{q^{BC}\sigma}(x^{BC})\nonumber\\
&=& g^{A||(B||C)}_{q \sigma}(x)
\end{eqnarray}

\begin{eqnarray}
a^{(A||B)||C}_{q \sigma}(x)&=&
 \big(a_{q^{AB} \sigma}(x^{AB}), a_{q^{C}
 \sigma}(x^{C})\big)\nonumber\\
&=&\big(a_{q^{A} \sigma}(x^{A}), a_{q^{B}
 \sigma}(x^{B}), a_{q^{C}
 \sigma}(x^{C})\big)\nonumber\\
&=&\big(a_{q^{A} \sigma}(x^{A}), a_{q^{BC}
 \sigma}(x^{BC})\big)\nonumber\\
&=&a^{A||(B||C)}_{q \sigma}(x)
\end{eqnarray}
